GWAS on a biobank-scale dataset

### 2017-07-27 GWAS-biobank-scale.Rmd
biobank-scale

---
title: "Imputation"
output: html_document
---

@@

```{r}
system.time(
  rdsfile <- snp_readBed(bedfile, backingfile = "tmp_biobank")
) # 1.6h
```

@@

```{r}
NCORES <- parallel::detectCores() / 2
# Get SNPs in long-range LD regions
system.time(
  ind.excl <- snp_indLRLDR(biobank$map$chromosome,
                           biobank$map$physical.pos)
)
# No parallelization for this huge dataset
system.time(
  ind.keep <- snp_clumping(biobank$genotypes, 
                           infos.chr = biobank$map$chromosome,
                           exclude = ind.excl,
                           ncores = 1)
) # 6.3h
```

@@

```{r}
# Parallelization is OK for PCA because 
# only a subset of this huge dataset is used 
system.time(
  obj.svd <- big_randomSVD(biobank$genotypes, 
                           fun.scaling = snp_scaleBinom(),
                           ind.col = ind.keep,
                           ncores = NCORES)
) # 2.4h
```

>>>>

---
title: "GWAS on a biobank-scale dataset"
output: html_document
---

@@

```{r}
system.time(
  rdsfile <- snp_readBed(bedfile, backingfile = "tmp_biobank")
) # 1.6h / 1h
```

@@

```{r}
NCORES <- parallel::detectCores() / 2
# Get SNPs in long-range LD regions
system.time(
  ind.excl <- snp_indLRLDR(biobank$map$chromosome,
                           biobank$map$physical.pos)
)
# No parallelization for this huge dataset
system.time(
  ind.keep <- snp_clumping(biobank$genotypes, 
                           infos.chr = biobank$map$chromosome,
                           exclude = ind.excl,
                           ncores = 1)
) # 6.3h / 5.4h
```

@@

```{r}
# Parallelization is OK for PCA because 
# only a subset of this huge dataset is used 
system.time(
  obj.svd <- big_randomSVD(biobank$genotypes, 
                           fun.scaling = snp_scaleBinom(),
                           ind.col = ind.keep,
                           ncores = NCORES)
) # 2.4h / 1.9h
```
